Biblioteca

```{r}
# Install required packages
install.packages("haven")
install.packages("dplyr")
install.packages("xts")
install.packages("zoo")
install.packages("DescTools")
install.packages("plm")
install.packages("reshape")
install.packages("tidyr")
install.packages("officer")
install.packages("flextable")
```

```{r Libraries}
library(dplyr)
library(xts)
library(zoo)
library(DescTools)
library(plm)
library(reshape)
library(tidyr)
library(officer)
library(flextable)
library(readxl)
library(openxlsx)
```


```{r}
data <- read_excel("C:/Users/phabi/Desktop/MESTRADO/FGV/Trabalho Final/Dados/Fingercrossed.xlsx")
#data$id <- seq_along(data$Identifier)  
```

Long Format

```{r}
data_long <- pivot_longer(data, 
                          cols = -Identifier,  # Selecting all columns except the company name
                          names_to = c(".value", "year"),  # Splitting the column names
                          names_sep = "_")  # Separator used in the column names
data_long <- data_long %>%
  mutate(year = as.numeric(year))

data_long <- data_long %>%
  arrange(Identifier, year)

```
Criando Age

```{r}
data_long <- data_long %>%
  group_by(Identifier) %>%  # Group by firm identifier
  arrange(Identifier, year) %>%  # Sort by firm and year
  mutate(PriceClose_NotNA = !is.na(PriceClose),  # Identify non-NA PriceClose years
         Age = if_else(PriceClose_NotNA, cumsum(PriceClose_NotNA), 0)) %>%  # Cumulative sum reset to 0 when NA
  ungroup()  # Remove groupin
```

Criando Size

```{r}
# Create Size and Size2 variables
data_long$Size <- log(data_long$TotalAssets)
data_long$Size2 <- data_long$Size^2
```

Calculando SA index

```{r}
library(naniar)

data_long <- data_long %>%
  replace_with_na(replace = list(Age = 0))
data_long <- data_long %>%
  replace_with_na(replace = list(`PropertyPlant&Equipment-Net-Total` = 0))
data_long <- data_long %>%
  replace_with_na(replace = list(`TotalLiabilities&Equity` = 0))
```


```{r}
data_long$SA <- (-0.737 * data_long$Size) + (0.043 * data_long$Size2) - (0.040 * data_long$Age)
```

Arrumando para o KZ

Tobin's Q = Item 6-60-74+(25*24) / 6
6 - liabilities and stockholders equity
60 - common equity
74 - Differed taxes
24 - Price Close
25 - Common Shares Outstanding

```{r}
data_long$Q <- (data_long$`TotalLiabilities&Equity`- data_long$`CommonEquity-Total`- data_long$`IncomeTaxes-Deferred` + (data_long$PriceClose * data_long$`CommonShares-Outstanding-Total`)) / data_long$`TotalLiabilities&Equity`
```

Cash Flow/K
(18+14)/8

```{r}
data_long$CashflowK <- (data_long$`IncomebeforeDiscontinuedOperations&ExtraordinaryItems` + data_long$`DepreciationDepletion&AmortizationTotal`) / data_long$`PropertyPlant&Equipment-Net-Total`
```

Debt/Total capital
(9+34)/(9+34+216)

34 = (data_long$TotalDebt - data_long$LongTermDebtTotal)

```{r}
data_long$DebtTotalCapital <- (data_long$LongTermDebtTotal + (data_long$TotalDebt - data_long$LongTermDebtTotal)) / (data_long$LongTermDebtTotal + (data_long$TotalDebt - data_long$LongTermDebtTotal) + data_long$StockholdersEquity)
```

Dividends/K
(21+19)/8
21+19 = Total dividends

```{r}
data_long$DividendK <- (data_long$`DividendsPaid-Cash-TotalCash Flow`) / data_long$`PropertyPlant&Equipment-Net-Total`
```

Cash/K
1/8

```{r}
data_long$CashK <- data_long$`Cash&ShortTermInvestments`/data_long$`PropertyPlant&Equipment-Net-Total`
```

KZ

Resolvendo o NA do KZ

```{r}
# Replace NA with 0 in specific columns if SA is non-NA
data_long <- data_long %>%
  mutate(
    CashflowK = ifelse(!is.na(SA) & is.na(CashflowK), 0, CashflowK),
    Q = ifelse(!is.na(SA) & is.na(Q), 0, Q),
    DebtTotalCapital = ifelse(!is.na(SA) & is.na(DebtTotalCapital), 0, DebtTotalCapital),
    DividendK = ifelse(!is.na(SA) & is.na(DividendK), 0, DividendK),
    CashK = ifelse(!is.na(SA) & is.na(CashK), 0, CashK)
  )
```

```{r}
data_long$KZ <- (-1.001909 * data_long$CashflowK + + 0.2826389*data_long$Q + +3.139193 * data_long$DebtTotalCapital - 39.3678 * data_long$DividendK - 1.314759 * data_long$CashK)
```

Limpando Data_long

```{r}
data_long <- data_long %>%
  select(-PriceClose_NotNA) %>%
  filter(rowSums(!is.na(select(., -Identifier))) > 0)
```

Clearing the dataset of middle NA's in the rows
Keeping only the years we want 1993-2022

```{r}
# Function to check for the pattern of having a non-NA followed by an NA and then a non-NA again
exclude_firms_with_na_pattern <- function(price_close) {
  # Find positions where PriceClose is not NA
  non_na_positions <- which(!is.na(price_close))
  # Loop through non-NA positions to find if an NA follows immediately after any of them
  for (pos in non_na_positions) {
    if (pos < length(price_close) && is.na(price_close[pos + 1]) && 
        any(non_na_positions > (pos + 1))) {
      return(TRUE)
    }
  }
  return(FALSE)
}

# Apply the function to filter out the firms
filtered_data <- data_long %>%
  group_by(Identifier) %>%
  filter(!exclude_firms_with_na_pattern(PriceClose)) %>%
  ungroup()

# Apply the function to filter out the firms
filtered_data <- filtered_data %>%
  group_by(Identifier) %>%
  filter(!exclude_firms_with_na_pattern(Size)) %>%
  ungroup()

filtered_data <- filtered_data %>%
  filter(year > 1992)
```

Dataset with only KZ and SA

```{r}
SAKZ <- filtered_data %>%
  select(Identifier, year, SA, KZ)
```

Limpando o SAKZ

```{r}
SAKZ <- SAKZ %>%
  filter(rowSums(!is.na(select(., -Identifier, -year))) > 0)
```

```{r}
SAKZ <- SAKZ %>%
  arrange(Identifier, year)
```

Correrlations 

```{r}
correlations_by_firm <- SAKZ %>%
  group_by(Identifier) %>%
  summarise(correlation = cor(SA, KZ, use = "complete.obs"))  # 'use' argument handles NAs

correlations_by_year <- SAKZ %>%
  group_by(year) %>%
  summarise(correlation = cor(SA, KZ, use = "complete.obs"))

total_correlation <- cor(SAKZ$SA,SAKZ$KZ)
```

Criando dataset para Regress찾o

 asset growth = market-to-book ratio, payout ratio, and ROA
 
```{r}
regressao <- filtered_data %>%
  select(Identifier,year,TotalAssets,PriceClose, `CommonShares-Outstanding-Total`, StockholdersEquity, `DividendsPaid-Cash-TotalCash Flow`, `NetIncome-Actual`, SA, KZ)
```

```{r}
regressao <- regressao %>%
  filter(rowSums(!is.na(select(., -Identifier, -year,-TotalAssets,-`CommonShares-Outstanding-Total`,-PriceClose,-StockholdersEquity,-`NetIncome-Actual`,-`DividendsPaid-Cash-TotalCash Flow`))) > 0)

regressao <- regressao %>%
  arrange(Identifier, year)

regressao$TotalAssets <- as.numeric(as.character(regressao$TotalAssets))
```

Criando os valores

Lagged Total Assets

```{r}
regressao <- regressao %>%
  group_by(Identifier) %>%
  mutate(LagTA = dplyr::lag(TotalAssets, 1))
```

Asset Grwoth

```{r}
regressao <- regressao %>%
  group_by(Identifier) %>%
  mutate(AssetGrowth = (TotalAssets - LagTA)/ LagTA)
```

Market to Book Ratio

```{r}
regressao <- regressao %>%
  group_by(Identifier) %>%
  mutate(MarkettoBookRatio = (PriceClose * `CommonShares-Outstanding-Total`)/ StockholdersEquity)
```

Payout Ratio

```{r}
#library(naniar)
regressao <- regressao %>%
  mutate(`DividendsPaid-Cash-TotalCash Flow` = replace(`DividendsPaid-Cash-TotalCash Flow`, is.na(`DividendsPaid-Cash-TotalCash Flow`), 0))
```

```{r}
regressao <- regressao %>%
  group_by(Identifier) %>%
  mutate(PayoutRatio = `DividendsPaid-Cash-TotalCash Flow`/ `NetIncome-Actual`)
```

ROA

```{r}
regressao <- regressao %>%
  group_by(Identifier) %>%
  mutate(ROA = `NetIncome-Actual`/TotalAssets)
```

Dataset s처 para Regress찾o

```{r}
regressao_msm <- regressao %>%
  select(Identifier, year, AssetGrowth, MarkettoBookRatio, PayoutRatio, ROA, KZ, SA)
```

Ajeitando Payout Ratio

```{r}
regressao_msm <- regressao_msm %>%
  mutate(PayoutRatio = replace(PayoutRatio, is.na(PayoutRatio), 0))
```

Regress찾o

```{r}
results_KZ <- plm(KZ ~ AssetGrowth + MarkettoBookRatio + PayoutRatio + ROA,
               data = regressao_msm, 
               index = c("Identifier", "year"),
               model = "within",
               effect = "twoways")

summary(results_KZ)
```

SA - index

```{r}
results_SA <- plm(SA ~ AssetGrowth + MarkettoBookRatio + PayoutRatio + ROA,
               data = regressao_msm, 
               index = c("Identifier", "year"),
               model = "within",
               effect = "twoways")

summary(results_SA)
```





















































